Fifteen years of decentralization attempts

### 2014-03-20 paper.tex
IEEE template comment is unneeded now

\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	% You must have at least 2 lines in the paragraph with the drop letter
	% (should never be an issue)
	With the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate. In many cases however, internet usage is either censored or monitored by third parties. In recent years the need for anonymous internet communication has become more apparent. Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.

>>>>

\section{Introduction}
	With the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate. In many cases however, internet usage is either censored or monitored by third parties. In recent years the need for anonymous internet communication has become more apparent. Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
